\Large \bf \projtitle

### 2015-05-05 doc/paper/paper.tex
some future work sections

The signa

@@

@@

>>>>

The signaling channel enables
% katie

@@

Implementing variation in requested chunk sizes could allow \zbf\ to independently
determine a more optimal chunk size for each asset. For instance, we hypothesize
that different chunk sizes are optimal for differently sized assets, and potentially
for different media types. If \zbf\ more intelligently determined the optimal size
of chunks for each resource, overall download latency would decrease.

@@

If \zbf\ could detect which peers have higher bandwidth connections, and thus
are more capable of swiftly delivering data to a client, \zbf\ could prioritize
requesting data from these peers. Perhaps \zbf\ could request larger chunks from
peers with higher bandwidth connections. \zbf\ could also dynamically react to
poor connections with peers during the chunk requesting process; chunk requests
that subsequently time out could be redistributed more intelligently among
peers with higher bandwidth connections.
